Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
paper beautification

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is $7.9$s, i.e., most controllers can be synthesized in less
than $17.2$ seconds.

@@

@@

Furthermore, it is practically relevant to consider constraints on the input
signal $u_{k}$ and bounds on the initial states $x_0$,
which we assume have given bounds. %%  $\overline{u}$, $\underline{u}$
%% and $\overline{x_0}$, $\underline{x_0}$, respectively.
We refer to these constraints as $\phi_{init}$:
$$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
\wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$$  
In the first case, this means that the control input saturates in view of
physical constraints.

@@

The following approximation errors will arise:
\begin{enumerate}
\item {\bf Truncation:}
Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.

So $\delta_T$ is the truncation error and it will propagate across operations.
\item {\bf Rounding:}
The following errors appear in simple operations. Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.
\begin{enumerate}
\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
\item Division: the operations performed by our controllers in the FWL domain do not include division, so these bounds are inconsequential to this paper. 
\end{enumerate}

>>>>

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is $7.9$ seconds, and most controllers can be synthesized in less
than $17.2$ seconds.

@@

\todo{Have we clarified anywhere the time domain of validity of our claims? CT vs DT? }

@@

Furthermore, it is practically relevant to consider constraints on the input
signal $u_{k}$ and bounds on the initial states $x_0$,
which we assume have given bounds. %%  $\overline{u}$, $\underline{u}$
%% and $\overline{x_0}$, $\underline{x_0}$, respectively.
We refer to these constraints as $\phi_{init}$: \todo{input constraints should not be called 'init'}
$$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
\wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$$  
In the first case, this means that the control input saturates in view of
physical constraints.

@@

The following approximation errors will arise:
\begin{enumerate}
\item {\bf Truncation:}
Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.

So $\delta_T$ is the truncation error and it will propagate across operations.
\item {\bf Rounding:}
The following errors appear in simple operations. Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.
\begin{enumerate}
\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
\item Division: the operations performed by our controllers in the FWL domain do not include division, so these bounds are inconsequential to this paper. 
\end{enumerate}
